fdcoexist

### 2018-09-04 meta_simulations.Rmd
Plots for R^2 & trait var for many trait seeds
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

first_simuls = future_map(1:60, function(x) {
    devtools::load_all()

    meta_simul(x) %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)
}) %>%
    bind_rows()

tictoc::toc()
```

>>>>

total_runs = 60

first_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x)
})
tictoc::toc()

first_simuls_r2 = first_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)) %>%
    bind_rows()

first_simuls_var = first_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))
```

```{r}
ggplot(first_simuls_r2, aes(scenario, r.squared)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width, cwm_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(uncor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    labs(subtitle = paste0("R2 of trait2 CWM ~ environment; N = ", total_runs),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
```

```{r}
ggplot(first_simuls_var, aes(scenario, var_value)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(var_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength")),
               scales = "free_y") +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(uncor    = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    labs(subtitle = paste0("Trait Variance across Patches; N = ", total_runs),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
```
